Tunnels to Towers: Secure Virtual Private Networking for CCN

### 2017-04-06 paper/05-sec-analysis.tex
times figure to paper

\textbf{Proof--} Suppose that Claim~\ref{theo1} is false. Then there exists a polynomial adversary $Adv$ capable of guessing the bit $b$ of Definition~\ref{def1} with non-negligible advantage, when given $I_e^b = Encapsulate(I_p^b)$ with $b \leftarrow \{0,1\}$ chosen at random. We show that if such adversary exists he can be used to construct a polinomial adversary $AdvCPA$ which breaks the CPA-security of $Enc_{pk}$. $AdvCPA$ plays the CPA-security game with a challenger sending him two messages $m^0$ and $m^1$. Following the CPA-security game, the challenger randomly chooses a value for the bit $b' \leftarrow \{0,1\}$ and gives back $C = Enc_{pk}(m^{b'})$ to $AdvCPA$. To break the CPA-security $AdvCPA$ must be able to guess the value of the bit $b'$ with non-negligible advantage. To that purpose $AdvCPA$ can query the challenger for the encryptions of $m^0$ and $m^1$ ($c^0 = Enc_{pk}(m^0)$ and $c^1 = Enc_{pk}(m^1)$) and then construct two interests $I_e^0 = createNewInterest(Gp_{name}, c^0)$ and $I_e^1 = createNewInterest(Gp_{name}, c^1)$, using the same $createNewInterest$ function used by algorithm~\ref{alg:interestEncap}, which is public (notice that $Gp_{name}$ is also public). Finally, $AdvCPA$ gives $I_e^0$ and $I_e^1$ as input to $Adv$ and outputs whatever $Adv$ outputs. Since under our assumption $Adv$ guesses the bit $b$ with non-negligible advantage, then $AdvCPA$ breaks the CPA-security of $Enc_{pk}$. But this violates the hypothesis of Claim~\ref{theo1} and, therefore, such $Adv$ cannot exist.

@@

\textit{Proof--}This follows directly from the definition of CCA security and the
argument in the above proof.

>>>>

\textit{\textbf{Proof--}} Suppose that Claim~\ref{theo1} is false. Then there exists a polynomial adversary $Adv$ capable of guessing the bit $b$ of Definition~\ref{def1} with non-negligible advantage, when given $I_e^b = Encapsulate(I_p^b)$ with $b \leftarrow \{0,1\}$ chosen at random. We show that if such adversary exists he can be used to construct a polinomial adversary $AdvCPA$ which breaks the CPA-security of $Enc_{pk}$. $AdvCPA$ plays the CPA-security game with a challenger sending him two messages $m^0$ and $m^1$. Following the CPA-security game, the challenger randomly chooses a value for the bit $b' \leftarrow \{0,1\}$ and gives back $C = Enc_{pk}(m^{b'})$ to $AdvCPA$. To break the CPA-security $AdvCPA$ must be able to guess the value of the bit $b'$ with non-negligible advantage. To that purpose $AdvCPA$ can query the challenger for the encryptions of $m^0$ and $m^1$ ($c^0 = Enc_{pk}(m^0)$ and $c^1 = Enc_{pk}(m^1)$) and then construct two interests $I_e^0 = createNewInterest(Gp_{name}, c^0)$ and $I_e^1 = createNewInterest(Gp_{name}, c^1)$, using the same $createNewInterest$ function used by algorithm~\ref{alg:interestEncap}, which is public (notice that $Gp_{name}$ is also public). Finally, $AdvCPA$ gives $I_e^0$ and $I_e^1$ as input to $Adv$ and outputs whatever $Adv$ outputs. Since under our assumption $Adv$ guesses the bit $b$ with non-negligible advantage, then $AdvCPA$ breaks the CPA-security of $Enc_{pk}$. But this violates the hypothesis of Claim~\ref{theo1} and, therefore, such $Adv$ cannot exist.

@@

\textit{\textbf{Proof--}} This follows directly from the definition of CCA security and the
argument in the above proof.

### 2017-04-06 paper/07-experiment.tex
Updates
times figure to paper

\section{Implementation and Performance Assessment}

@@

@@

The experiments presented throughout this section were executed in an Intel Core i7-3770 octacore CPU @3.40GHz, with 16GB of RAM, running Linux (Ubuntu 14.04LTS). Content payload sizes were set to 10 kilobytes.
On every experiment, each of the two gateway processes (i.e., consumer side gateway process, and producer side gateway process) were assigned as a high priority processes and each of them ran in a single core of the processor.
Table~\ref{should_be_figure} (\todo{Should be a single figure w/ six boxplots}) presents boxplots for the execution times of the four algorithms involved in CCVPN's data transmission, including both, PKE and Symm. Key versions for interest encapsulation and decapsulation.

\begin{table}[!h]
\centering
\caption{Interest encapsulation processing times}
\label{should_be_figure}
\begin{tabular}{|l|l|l|l|l|}
\hline
Encapsulation mode   & Encapsulation & Decapsulation \\ \hline
Public Key  & 444$\mu s$           & 449$\mu s$           \\ \hline \cline{4-5} 
Symmetric Key & TODO          & TODO          \\ \hline
\end{tabular}
\end{table}

\begin{table}[!h]
\centering
\caption{Content encryption and decryption times for different payload sizes}
\label{my-label}
\begin{tabular}{|l|l|l|}
\hline
Packet size        & Encryption & Decryption \\ \hline
$1024$B & 125$\mu s$        & 193$\mu s$        \\ \hline
$4096$B & 141$\mu s$        & 220$\mu s$        \\ \hline
$16384$B & 220$\mu s$        & 367$\mu s$        \\ \hline
$65536$B & 519$\mu s$        & 702$\mu s$        \\ \hline
\end{tabular}
\end{table}

@@

To investigate the processing overhead we measure the average time demand for computing the interests' encapsulation (in public and symmetric key versions), interest decapsulation, content encryption, and content decryption for different content packet sizes (1024, 4096, 16384, and 65536 bytes). We also measure the state consumption for these same four functions.

To compute the overall network throughput we measure the average data-rate for transmissions of 1 to 1,000,000 different interests issues per consumer. We also vary the number of consumers and producers from 1 to 10 of each. Finally, in addition to the network throughput, we also exhibit the total transmission delay for each of the experiments.

@@

\begin{figure}[]
\centering
  \subfigure[Throughput]{\includegraphics[width=0.49\columnwidth]{images/1_1_thput.pdf}\label{1a}}
  \hfil
  \subfigure[Avg. RTT]{\includegraphics[width=0.49\columnwidth]{images/1_1_rtt.pdf}\label{1b}}
\caption{CCVPN performance with one consumer and one producer for increasing interest issuance rates.}\label{exp1}
\end{figure}

\begin{figure}[]
\centering
  \subfigure[Throughput]{\includegraphics[width=0.49\columnwidth]{images/n_1_thput.pdf}\label{1a}}
  \hfil
  \subfigure[Avg. RTT]{\includegraphics[width=0.49\columnwidth]{images/n_1_rtt.pdf}\label{1b}}
\caption{CCVPN performance with multiple consumers and one producer. Each consumer requests with 1 mbps rate.}\label{exp1}
\end{figure}

\begin{figure}[]
\centering
  \subfigure[Throughput]{\includegraphics[width=0.49\columnwidth]{images/n_n_thput.pdf}\label{1a}}
  \hfil
  \subfigure[Avg. RTT]{\includegraphics[width=0.49\columnwidth]{images/n_n_rtt.pdf}\label{1b}}
\caption{CCVPN performance with multiple consumers and multiple producers. Each consumer requests with 1 mbps rate.}\label{exp1}
\end{figure}

>>>>

\section{Implementation and Performance Assessment}\label{sec:exp}

@@

\begin{figure}[]
\centering
\includegraphics[width=\columnwidth]{images/times.pdf}
\caption{Execution time of the algorithms in CCVPN design}\label{times}
\end{figure}

\begin{figure}[]
\centering
  \subfigure[Throughput]{\includegraphics[width=0.8\columnwidth]{images/1_1_thput.pdf}\label{1a}}
  \hfil
  \subfigure[Avg. RTT]{\includegraphics[width=0.8\columnwidth]{images/1_1_rtt.pdf}\label{1b}}
\caption{CCVPN performance with one consumer and one producer for increasing interest issuance rates.}\label{exp1}
\end{figure}

\begin{figure}[]
\centering
  \subfigure[Throughput]{\includegraphics[width=0.8\columnwidth]{images/n_1_thput.pdf}\label{1a}}
  \hfil
  \subfigure[Avg. RTT]{\includegraphics[width=0.8\columnwidth]{images/n_1_rtt.pdf}\label{1b}}
\caption{CCVPN performance with multiple consumers and one producer. Each consumer requests with 1 mbps rate.}\label{exp1}
\end{figure}

\begin{figure}[]
\centering
  \subfigure[Throughput]{\includegraphics[width=0.8\columnwidth]{images/n_n_thput.pdf}\label{1a}}
  \hfil
  \subfigure[Avg. RTT]{\includegraphics[width=0.8\columnwidth]{images/n_n_rtt.pdf}\label{1b}}
\caption{CCVPN performance with multiple consumers and multiple producers. Each consumer requests with 1 mbps rate.}\label{exp1}
\end{figure}

@@

The experiments presented throughout this section were executed in an Intel Core i7-3770 octacore CPU @3.40GHz, with 16GB of RAM, running Linux (Ubuntu 14.04LTS). Content payload sizes were set to 10 kilobytes.
On every experiment, each of the two gateway processes (i.e., consumer side gateway process, and producer side gateway process) were assigned as a high priority processes and each of them ran in a single core of the processor.
Fig.~\ref{times} presents boxplots for the execution times of the four algorithms involved in CCVPN's data transmission, including both, PKE and Symm. Key versions for interest encapsulation and decapsulation.

@@

\subsection{Discussion}

@@

### 2017-04-06 paper/ccvpn.tex
times figure to paper

\begin{abstract}
Content Centric Networking (CCN) is a future Internet architecture which is envisioned as an alternative to the current IP-based model. CCN emphasizes content distribution by making contents directly addressable in a request-based information centric network. An advantage of CCN is that it has some innate privacy friendly features, such as lack of source and destination addresses in packets. However, to be considered a viable future Internet architecture, CCN must offer services for private and anonymous communication that are at least equivalent for  to those present in the IP architecture. Among such, VPNs are a very popular application that enables users to send and receive data across shared or public networks as if their computing devices were directly connected to the same private network. In this work we design, implement and evaluate CCVPN, a content centric virtual private network capable of providing the same functionality of VPNs within the CCN Internet architecture. To the best of our knowledge CCVPN is the first proposal of a VPN alike service for CCNs. In addition to the CCVPN design, we also provide a security analysis and experimental performance evaluation for this new system.
\end{abstract}

>>>>

\begin{abstract}
Content Centric Networking (CCN) is a future Internet architecture which is envisioned as an alternative to the current IP-based model. CCN emphasizes content distribution by making contents directly addressable in a request-based information centric network. An advantage of CCN is that it has some innate privacy friendly features, such as lack of source and destination addresses in packets. However, to be considered a viable future Internet architecture, CCN must offer services for private and anonymous communication that are at least equivalent to those present in the IP architecture. Among such, VPNs are a very popular application that enables users to send and receive data across shared or public networks as if their computing devices were directly connected to the same private network. In this work we design, implement and evaluate CCVPN, a content centric virtual private network capable of providing the same functionality of VPNs within the CCN Internet architecture. To the best of our knowledge CCVPN is the first proposal of a VPN alike service for CCNs. In addition to the CCVPN design, we also provide a security analysis and experimental performance evaluation for this new system.
\end{abstract}
